Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-28 paper/ms.tex
abstract+results sections are updated

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the observational geometries. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host one LAE with a
probability $f_{\rm occ}$. We find that the large scatter in the mocks, induced by
cosmic variance, makes the number density and spatial clustering
information insufficient to derive a unique and narrow set of values
for the parameters in the model. In particular, it is always possible
to find a model that is consistent with observations and has any
desired occupation fraction in the range $0.1\leq f_{\rm occ}\leq 1.0$
.  Nevertheless, in the models we can define three different families
of parameters based on their mass range, $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, and occupation fraction,
$f_{\rm occ}$. The dominant family is composed by models with a narrow
mass range $\Delta M<1.0$ dex, a low occupation fraction $f_{\rm
  occ}\leq 0.3$ and a maximum mass $M_{\rm  max}< 10^{12}$\hMsun.  The
existence of this dominant family gives support to the idea that the
most massive dark matter halos at that epoch do not host the brightest
LAEs and that only a small fraction of star forming galaxies can be
actually detected as LAEs.
\end{abstract}

@@

This \documentname is structured as follows. In the next section we present
the simulation and model used to produce the mock catalogs and the criteria
we use to compare them against observations. In \SS \ref{sec:results} we
present the main results for the halo mass and occupation fraction. We
continue with a discussion of these results under the light of other
observational and theoretical results. Finally, we present our
conclusions in \SS
\ref{sec:conclusions}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_maxden.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} and
\citet{Ouchi2010}. The error bars in the   theoretical data correspond
to the standard deviation from the different mocks surveys. 
%Right:
%Same results in the $\theta_{0}$-$M_{\rm min}$ plane, with the
%observational constraint on $\theta_{0}$ epresented by the red
%rectangle. Blue  squares represent models with $\log_{10} M_{\rm
%  max}<12.0$, green circles correspond to models with $\log_{10}
%M_{\rm max}>12.0$. 
\label{fig:correlation_parameters}}
\end{figure*}

@@

In the left panel Figure \ref{figure:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} (green dot)
is successful in reducing the total number of possible models. Only
those with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
reproduce observations. {\bf Cual es el resultsdo de Ouchi
  para $\theta_0$?}

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
for the {\tt match} method. To make this selection we consider that
a model is consistent with observations if there is a $1-\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$ . Comparing this Figure with the results shown in Figure
\ref{fig:restriction_mock} we see that the models that were removed
were those with highest minimal masses $M_{\rm min}>10^{11.2}$, for
all the values of $M_{\rm max}$, with preferentially high
occupation fractions of $f_{\rm occ}> 0.5$.

We conclude that the clustering information is able to put meaningful
constraints on the values of the maxium mass parameters $M_{\rm max}$
and the occupation fraction $f_{\rm occ}$.

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the observational geometries. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one LAE with a probability $f_{\rm occ}$.  We find that the observational information on the number density restricts the minimum mass to a
range $10^{10}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ leaving all the
other parameters unrestricted, while the clustering information puts a
tight constraint of $M_{\rm   max}<10^{12}\hMsun$. This gives support
to the idea that the most massive dark matter halos at that epoch do
not host the brightest LAEs.  However, none of these observations is
able to constrain the occupation fraction. It is always possible to
find a model that is consistent with observations and has any desired
occupation fraction in the range $0.1\leq f_{\rm occ}\leq
1.0$. Furthermore, all models have a mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex. 
We divide the best models into families of low and high occupation
fraction with a transition around $f_{\rm occ}\leq 0.3$. These two
families are almost disjoint in their values of $M_{\rm min}$. Low
occupation fraction occurs below a threshold of $M_{\rm th}=
10^{10.8}\Msun$, while high occupation fractions are present in
$M_{\rm min}>M_{\rm the}$. These two families of models are
similar in size, giving an unconclusive response as to which is the
occupation fraction of LAEs at $z=3.1$. A conclusive answer requires
a detailed physical model for the  connection between dark matter,
star formation and the escape of \ly radiation. That kind of modelling
should also provide a plausible explanation for the narrow range in
mass $\Delta M<1.0$ dex derived here for the halos hosting LAEs at
$z=3.1$.

\end{abstract}

@@

This \documentname is structured as follows. In the next section we present
the simulation and model used to produce the mock catalogs and the criteria
we use to compare them against observations. In \S \ref{sec:results} we
present the main results for the halo mass and occupation fraction. We
continue with a discussion of these results under the light of other
observational and theoretical results. Finally, we present our
conclusions in \S \ref{sec:conclusions}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_maxden.pdf} 
\hspace{5mm}  
\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
\end{center}
\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Hayashino2004} and
\citet{Ouchi2010}. The error bars in the   theoretical data correspond
to the standard deviation from the different mocks surveys. 
\label{fig:correlation_parameters}}
\end{figure*}

@@

In the left panel Figure \ref{figure:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} (green dot)
is successful in reducing the total number of possible models. Only
those with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
reproduce observations. The right panel of Figure
\ref{figure:correlation_parameters} shows the results for fields in
the mock catalog that have an average number density that are compared
against the fit of the data reported by \cite{Ouchi2010}. In this case
we find that there are large uncertainties in the observational data,
however it is possible to discard a fraction of the models.

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
both for the comparisong against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1-\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not succeed in
greatly reducing the number of models.

At this point we keep the models that are consistent with both
observational constraints. This basically reduces the selection to the
models already restricted by the data in \cite{Hayashino2004} as
presented in the lower panels of Figure
\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
this comparison is that clustering information is able to put
meaningful constraints on the values of $M_{\rm max}$. However, the
possible values for the occupation fraction are still in the initial
range $0.1\leq f_{\rm occ}\leq 1$.
